E1: ENRON Sentiment

### 2016-04-01 paper/paper.tex
fix long table

Furthermore, email datasets usually come in a semi-structured fashion in the sense that the actual data might not be well formed. 
For instance, recipients attributes and email's body can be difficult to parse.
Thus, the analysis should include some validation steps which increase the complexity of the whole process.

@@

In Table \ref{tab:corr} is an ordered (by correlation between sentiment and
stock prices) list of mailboxes. The rightmost column denotes the number of
data points used to compute the correlation, that is the number of days in which
we have both sentiment and stock prices information.
We show in Figures \ref{fig:sentiment_vs_stock_buy} and
\ref{fig:sentiment_dist_hist_buy} an example of positive correlation of
sentiment and stock prices for the mailbox \texttt{buy-r}. In Figures
\ref{fig:sentiment_vs_stock_giron} and \ref{fig:sentiment_dist_hist_giron}
instead we show an example of negative correlation for the mailbox
\texttt{giron-d}.

@@

\begin{appendix}
% FIXME: table is kinda broken

@@

@@

bass-e         &                -0.000 &     381 \\
mclaughlin-e   &                -0.001 &     339 \\
beck-s         &                -0.003 &     470 \\
weldon-c       &                -0.004 &     205 \\
cash-m         &                -0.005 &     334 \\
watson-k       &                -0.007 &     220 \\
solberg-g      &                -0.008 &      78 \\
schoolcraft-d  &                -0.009 &     166 \\
scott-s        &                -0.012 &     454 \\
arnold-j       &                -0.013 &     317 \\
hain-m         &                -0.015 &     179 \\
davis-d        &                -0.015 &     242 \\
dasovich-j     &                -0.019 &     517 \\
neal-s         &                -0.021 &     268 \\
shively-h      &                -0.021 &     208 \\
gilbertsmith-d &                -0.022 &     152 \\
lay-k          &                -0.023 &     318 \\
slinger-r      &                -0.032 &      58 \\
fossum-d       &                -0.037 &     270 \\
sanchez-m      &                -0.037 &      45 \\
lokay-m        &                -0.039 &     436 \\
shapiro-r      &                -0.040 &     294 \\
ring-r         &                -0.040 &     116 \\
delainey-d     &                -0.040 &     203 \\
hodge-j        &                -0.041 &     124 \\
mccarty-d      &                -0.045 &      96 \\
carson-m       &                -0.046 &     193 \\
jones-t        &                -0.049 &     574 \\
campbell-l     &                -0.052 &     428 \\
harris-s       &                -0.054 &      46 \\
germany-c      &                -0.059 &     534 \\
horton-s       &                -0.061 &     236 \\
king-j         &                -0.063 &      59 \\
sager-e        &                -0.066 &     485 \\
farmer-d       &                -0.066 &     524 \\
williams-j     &                -0.067 &     120 \\
causholli-m    &                -0.069 &      89 \\
scholtes-d     &                -0.070 &     162 \\
tycholiz-b     &                -0.076 &     154 \\
hyatt-k        &                -0.078 &     261 \\
griffith-j     &                -0.081 &     209 \\
lavorato-j     &                -0.089 &     359 \\
schwieger-j    &                -0.093 &     160 \\
derrick-j      &                -0.098 &     180 \\
hyvl-d         &                -0.111 &     361 \\
stokley-c      &                -0.125 &     137 \\
mann-k         &                -0.127 &     346 \\
corman-s       &                -0.131 &     184 \\
rapp-b         &                -0.132 &      57 \\
gang-l         &                -0.134 &      76 \\
panus-s        &                -0.136 &      49 \\
staab-t        &                -0.147 &      92 \\
geaccone-t     &                -0.148 &     142 \\
ybarbo-p       &                -0.167 &     145 \\
maggi-m        &                -0.175 &      85 \\
cuilla-m       &                -0.178 &     123 \\
edrm-enron-v2  &                -0.179 &     202 \\
merris-s       &                -0.180 &      36 \\
giron-d        &                -0.193 &     344 \\
salisbury-h    &                -0.198 &     211 \\
badeer-r       &                -0.199 &      76 \\
motley-m       &                -0.199 &     100 \\
ermis-f        &                -0.241 &     118 \\
hernandez-j    &                -0.262 &     300 \\
dean-c2        &                -0.273 &      85 \\
dean-c         &                -0.329 &     187 \\
kaminski-v     &                   NaN &       0 \\
kean-s         &                   NaN &       0 \\

@@

\label{tab:corr}

@@

\input{corrleation_per_user_table.txt}

>>>>

Furthermore, email datasets usually come in a semi structured fashion in the sense that the actual data might not be well formed. 
For instance, recipients attributes and email's body can be difficult to parse.
Thus, the analysis should include some validation steps which increase the complexity of the whole process.

@@

In Table $7$ and Table $8$ is an ordered (by correlation between sentiment and
stock prices) list of mailboxes. The rightmost column denotes the number of
data points used to compute the correlation, that is the number of days in which
we have both sentiment and stock prices information.
We show in Figures \ref{fig:sentiment_vs_stock_buy} and
\ref{fig:sentiment_dist_hist_buy} an example of positive correlation of
sentiment and stock prices for the mailbox \texttt{buy-r}. In Figures
\ref{fig:sentiment_vs_stock_giron} and \ref{fig:sentiment_dist_hist_giron}
instead we show an example of negative correlation for the mailbox
\texttt{giron-d}.

@@

\clearpage
\begin{appendix}

@@

%\label{tab:corr_pos}

@@

bass-e         &                 0.000 &     381 \\

@@

@@

\clearpage
\begin{supertabular}{ l r r }
%\label{tab:corr_neg}
\toprule
{} &  stock\_sentiment\_corr &  points \\
\midrule
mclaughlin-e   &                -0.001 &     339 \\
beck-s         &                -0.003 &     470 \\
weldon-c       &                -0.004 &     205 \\
cash-m         &                -0.005 &     334 \\
watson-k       &                -0.007 &     220 \\
solberg-g      &                -0.008 &      78 \\
schoolcraft-d  &                -0.009 &     166 \\
scott-s        &                -0.012 &     454 \\
arnold-j       &                -0.013 &     317 \\
hain-m         &                -0.015 &     179 \\
davis-d        &                -0.015 &     242 \\
dasovich-j     &                -0.019 &     517 \\
neal-s         &                -0.021 &     268 \\
shively-h      &                -0.021 &     208 \\
gilbertsmith-d &                -0.022 &     152 \\
lay-k          &                -0.023 &     318 \\
slinger-r      &                -0.032 &      58 \\
fossum-d       &                -0.037 &     270 \\
sanchez-m      &                -0.037 &      45 \\
lokay-m        &                -0.039 &     436 \\
shapiro-r      &                -0.040 &     294 \\
ring-r         &                -0.040 &     116 \\
delainey-d     &                -0.040 &     203 \\
hodge-j        &                -0.041 &     124 \\
mccarty-d      &                -0.045 &      96 \\
carson-m       &                -0.046 &     193 \\
jones-t        &                -0.049 &     574 \\
campbell-l     &                -0.052 &     428 \\
harris-s       &                -0.054 &      46 \\
germany-c      &                -0.059 &     534 \\
horton-s       &                -0.061 &     236 \\
king-j         &                -0.063 &      59 \\
sager-e        &                -0.066 &     485 \\
farmer-d       &                -0.066 &     524 \\
williams-j     &                -0.067 &     120 \\
causholli-m    &                -0.069 &      89 \\
scholtes-d     &                -0.070 &     162 \\
tycholiz-b     &                -0.076 &     154 \\
hyatt-k        &                -0.078 &     261 \\
griffith-j     &                -0.081 &     209 \\
lavorato-j     &                -0.089 &     359 \\
schwieger-j    &                -0.093 &     160 \\
derrick-j      &                -0.098 &     180 \\
hyvl-d         &                -0.111 &     361 \\
stokley-c      &                -0.125 &     137 \\
mann-k         &                -0.127 &     346 \\
corman-s       &                -0.131 &     184 \\
rapp-b         &                -0.132 &      57 \\
gang-l         &                -0.134 &      76 \\
panus-s        &                -0.136 &      49 \\
staab-t        &                -0.147 &      92 \\
geaccone-t     &                -0.148 &     142 \\
ybarbo-p       &                -0.167 &     145 \\
maggi-m        &                -0.175 &      85 \\
cuilla-m       &                -0.178 &     123 \\
edrm-enron-v2  &                -0.179 &     202 \\
merris-s       &                -0.180 &      36 \\
giron-d        &                -0.193 &     344 \\
salisbury-h    &                -0.198 &     211 \\
badeer-r       &                -0.199 &      76 \\
motley-m       &                -0.199 &     100 \\
ermis-f        &                -0.241 &     118 \\
hernandez-j    &                -0.262 &     300 \\
dean-c2        &                -0.273 &      85 \\
dean-c         &                -0.329 &     187 \\
kaminski-v     &                   NaN &       0 \\
kean-s         &                   NaN &       0 \\
\bottomrule
\end{supertabular}
